Variable Density Tesseroids: Gravity fields calculation in spherical coordinates using variable densities in depth

### 2017-10-31 manuscript/manuscript.tex
Reorganized manuscript folder. Fixed Makefile to work properly
Changes in manuscript

The distance-size ratio determinations have been made through the comparison of the numerical approximations with the analytical solutions for the a spherical shell with variable density, which had to be analytically obtained.
From the wide range of possible density variations, we've chosen a linear, an exponential and a discontinuous density functions.
These comparisons have been made without applying the density-based discretization algorithm in order to isolate the former one.
The tests over the first two functions have shown that values of $D$ equal to 1, 2 and 8 for the calculation of the gravity potential, its gradient and the Marussi tensor components, respectively, produce an accuracy of 0.1\% or better.
On the other hand, the algorithm on its own does not guarantee this amount of accuracy in case of highly varying exponential functions or discontinuous densities.

We have performed similar tests for the density-based discretization algorithm comparing the numerical model with the analytical solutions for a spherical shell with various exponential densities: from a low varying to a high varying one.
Each comparison was made for different values of $\delta$, keeping the default values of $D$ previously obtained.
This tests have shown that a value of $\delta = 0.2$ guarantees an accuracy of 0.1\% or better on every case, while the same results can be obtained performing this tests with the discontinuous density function.

@@

\bibliographystyle{gji}
\bibliography{bibtex/references}

>>>>

The distance-size ratio determinations have been made through the comparison of the numerical approximations with the analytical solutions for the a spherical shell with variable density, which had to be analytically obtained.
These tests have been made without applying the density-based discretization algorithm in order to isolate the former one.
From the wide range of possible density variations, we've chosen a linear, an exponential and a discontinuous density functions.
The comparisons over the first two functions have shown that values of $D$ equal to 1, 2 and 8 for the calculation of the gravity potential, its gradient and the Marussi tensor components, respectively, produce an accuracy of 0.1\% or better.
On the other hand, the algorithm on its own does not guarantee this amount of accuracy in case of highly varying exponential functions or discontinuous densities.

We have performed similar tests for the density-based discretization algorithm comparing the numerical model with the analytical solutions for a spherical shell with various exponential densities: from low varying to high varying functions.
Each comparison was made for different values of $\delta$, keeping the default values of $D$ previously obtained.
This tests have shown that a value of $\delta = 0.2$ guarantees an accuracy of 0.1\% or better on every case, while the same results can be obtained performing this tests with the discontinuous density function.

Moreover, we had performed speed comparisons between tesseroids models with homogeneous and variable densities, showing that a high varying density function requires more computation time than a low varying one, as expected.

@@

\bibliographystyle{gji}
\bibliography{references}
